The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex
Minor changes
Typos fixed.

o10 = true
\end{MyVerbatim}
}
\medspace

>>>>

o10 = true
\end{MyVerbatim}
}
\medspace
There is one other relevant special algorithm which checks whether the polynomial $f$ factors as a product of functions $f = \prod_i f_i^{a_i}$ that are in simple normal crossing with each other (in which case, the $F$-pure threshold is just the minimum of the $1/a_i$ as mentioned above).  Recall that a set of elements $\{f_i\}$ are said to be in simple normal crossing at a point, if locally, the $f_i$ form part of a regular system of parameters.  We verify this by looking at the jacobian matrix of each the subsets of the $f_i$ (evaluated at the origin) and checking that these matrices have the expected rank.  We also verify that these subsets generate ideals of the correct height.  Note, this calls {\tt factor f}, which may be slow.  The user can turn off this factorization call with {\tt UseSpecialAlgorithms => false}.

This calls the function {\tt isSimpleNormalCrossing} which is also exposed to the user.  Note, if one sets the {\tt IsLocal => true} option, the {\tt isSimpleNormalCrossing} function checks that the $f_i$ are in simple normal crossing everywhere, which can be much slower (as jacobian ideals are computed).
